Extended Abstract

### 2021-07-28 paper/paper.tex
Add comments on related work

To the best of our knowledge, this problem has not yet been mechanised, and has only been treated in Padovani's work on type reconstruction for composite types \cite{Padovani15}.
With this work, we aim to:
\begin{itemize}
  \item State and prove clear soundness and completeness theorems for both constraint collection and constraint resolution (\autoref{inference}).
  \item Mechanise in Agda the totality of this work.
\end{itemize}

>>>>

Decidable (and certified) type checking procedures have been provided for a range of linear type systems \cite{Allais15,Allais17,OrchardLE19,Brady21}.
These type systems however do not deal with types containing usage annotations nested within: in our case, a channel with \emph{payload} type ``channel with input usage 0'' differs in type from a channel with payload type ``channel with input usage 1''.
As a result, we must roll typing inference and linearity inference into one, and deal with the type polymorphism that arises as a result of usage polymorphism.
To the best of our knowledge, this problem has not yet been mechanised, and has only been treated in Padovani's work on type reconstruction for composite types \cite{Padovani15}.
With this work, we aim to:
\begin{itemize}
  \item State and prove clear soundness and completeness theorems for both constraint collection and constraint resolution (\autoref{inference}).
  \item Mechanise in Agda the totality of this work.
\end{itemize}
